Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-14 chi2012.tex
prestudy introductory ditty in place

%% not sure where this goes >> but i want to keep it

Setting out to investigate the potential role for better support for data integration in PIM, we first sought an updated understanding of how and whether people still used multiple information sources in the course of everyday information-related activities. There were several reasons for this inquiry; first, we wondered whether people were increasingly relying only on the handful of the massive ``supersites'' (Facebook, Google, Wikipedia) for most of their activities than actually searching for distributed sources of information.  If this were the case, much of the benefit could be gained by merely integrating PIM tools with the handful of sites, rather than the substantially more challenging problem of integrating data from arbitrary information sources on the Web.  Second, if people did rely on multiple sites, we wished to know why, and the typical kinds of tasks people did that required diverse information collection - were these kinds of tasks rare?  If so, this would suggest that perhaps specialised interfaces could be concocted for this purpose rather than it being a PIM need.

@@

\subsection{PS.1 - Understanding Data Diversity in Everyday Tasks}
\subsubsection{Method}
Our pre-study investigated the types of tasks people perform online that required heterogeneous data sources, and which tools they would use to organise a large social event involving 15 or more people.  We interviewed 8 participants, using a general interview guide approach based loosely on a set of questions (see Appendix ?).  This approach allowed both the participant and interviewer a degree of freedom in conversation and each interview could adapt to the participant’s experiences, while collecting the same general areas of information.  Each interview was recorded and notes taken, the interviewer was trained so that they were knowledgeable about the importance of the study and to minimise bias.

>>>>

%% not sure where this goes >> but i want to keep it
Setting out to investigate the potential role for better support for data integration in PIM, we first sought an updated understanding of how and whether people still used multiple information sources in the course of everyday information-related activities. There were several reasons for this inquiry; first, we wondered whether people were increasingly relying only on the handful of the massive ``supersites'' (Facebook, Google, Wikipedia) for most of their activities than actually searching for distributed sources of information.  If this were the case, much of the benefit could be gained by merely integrating PIM tools with the handful of sites, rather than the substantially more challenging problem of integrating data from arbitrary information sources on the Web.  Second, if people did rely on multiple sites, we wished to know why, and the typical kinds of tasks people did that required diverse information collection - were these kinds of tasks rare?  If so, this would suggest that perhaps specialised interfaces could be concocted for this purpose rather than it being a PIM need.

@@

\subsection{PS.1 - Understanding Data Diversity in Everyday Tasks}
% \subsubsection{Method}
Our pre-study investigated the types of tasks people perform online that required heterogeneous data sources, and which tools they would use to organise a large social event involving 15 or more people.  We interviewed 8 participants, using a general interview guide approach based loosely on a set of questions (see Appendix ?).  This approach allowed both the participant and interviewer a degree of freedom in conversation and each interview could adapt to the participant’s experiences, while collecting the same general areas of information.  Each interview was recorded and notes taken, the interviewer was trained so that they were knowledgeable about the importance of the study and to minimise bias.
